Clean data

### 2019-06-25 analysis/02_clean-data.Rmd
Cleaned up transformations (including base cases)

data %>% 

@@

@@

@@

@@

@@

@@

    # - Once every few years → Rarely (base case)

@@

@@

@@

        Q5.4 == 5 ~ "Not involved"

@@

@@

    # - Don't know → NULL

@@

        Q5.8 == 7 ~ "NULL"

@@

@@

>>>>

data <- data %>% 

@@

      levels = c("Rarely", "Once a week", "At least once a day")

@@

      levels = c("Not often", "Often")

@@

    # - Once a year → More than once a month, less than once a year (base case)

@@

      levels = c("More than once a month, less than once a year", "At least once a month")

@@

    # - NA → Haven't volunteered in past 12 months (base case)

@@

    # - Once every few years → Rarely

@@

        is.na(Q2.10) == TRUE ~ "Haven't volunteered in past 12 months",

@@

      levels = c("Haven't volunteered in past 12 months", "Rarely", "More than once a month, less than once a year", "At least once a month")

@@

        Q5.4 == 5 ~ "Not involved",
      levels = c("Not involved", "Involved")

@@

      levels = c("Not involved", "Involved")

@@

    # - Don't know → Not sure

@@

        Q5.8 == 7 ~ "Not sure"
      levels = c("Not sure", "Rarely", "At least once a month")

@@

      levels = c("Not important", "Important")

@@

      levels = c("Less than median", "More than median")
